Enhancing \Hinf{} Norm Estimation using Local LPM/LRM Modeling: Applied to an AVIS\thanksref{thx}

### 2016-04-01 ch04-lrmhinf/ch04appendices.inc.tex
Add Axes of AVIS

In the top-level model (\figref{fig:avis:simulink:setup}), all signals are six-dimensional and each element corresponds to a mechanical degree-of-freedom of the \gls{AVIS}, i.e.
\begin{enumerate}
  \item the translational velocity in $x$ direction (horizontal),
  \item the translational velocity in $y$ direction (horizontal),
  \item the translational velocity in $z$ direction (vertical),
  \item the rotational velocity around the $x$ axis,
  \item the rotational velocity around the $y$ axis,
  \item the rotational velocity around the $z$ axis.
\end{enumerate}
In the main text, we have simplified this system to consider only the translation in the vertical direction (i.e. the third signal).
For the other directions, the applied signals (\code{r1} and \code{r2}) were set to $0$.
However, inside the feedback loop, all directions are controlled by the experimental controller $\experimental\Controller$.

>>>>

In the top-level model (\figref{fig:avis:simulink:setup}), all signals are six-dimensional and each element corresponds to a mechanical degree-of-freedom of the \gls{AVIS}, i.e.
\begin{enumerate}
  \item the translational velocity in $x$ direction (horizontal),
  \item the translational velocity in $y$ direction (horizontal),
  \item the translational velocity in $z$ direction (vertical),
  \item the rotational velocity around the $x$ axis,
  \item the rotational velocity around the $y$ axis,
  \item the rotational velocity around the $z$ axis.
\end{enumerate}
The axes are indicated in \figref{fig:avis:withAxes}.

\begin{figure}
  \centering
  \includegraphics{\thisDir/figs/avis-with-axes.pdf}
  \caption{\glsentrytext{AVIS} with $(x,y,z)$ coordinate frame indicated and bird's eye view of the approximate locations of the actuators and sensors. For each of the actuators and sensors, the color indicates the principal direction}
  \label{fig:avis:withAxes}
\end{figure}

In the main text, we have simplified this system to consider only the translation in the vertical direction (i.e. the third signal).
For the other directions, the applied signals (\code{r1} and \code{r2}) were set to $0$.
However, inside the feedback loop, all directions are controlled by the experimental controller $\experimental\Controller$.
